### 2021-06-09 paper/medical_parameters.tex
Simplify medical parameters section and hopefully fix references.

\subsubsection{Duration until Infectiousness and Symptoms}

@@

\subsubsection{Duration of Infectiousness}

We assume that the duration of infectiousness is the same for both symptomatic and
asymptomatic individuals as evidence suggests little differences in the transmission
rates between symptomatic and asymptomatic patients
(\citet{Yin2020}) and that the viral load between symptomatic and asymptomatic
individuals are similar (\citet{Zou2020}, \citet{Byrne2020}, \citet{Singanayagam2020}).

Our distribution of the duration of infectiousness is based on \citet{Byrne2020}.

For symptomatic cases they arrive at zero to five days before symptom onset (figure 2)
and three to eight days of infectiousness afterwards.\footnotemark Thus, we arrive at 0
to 13 days as the range for infectiousness among individuals who become symptomatic (see
also figure 5).

\footnotetext{Viral loads may be detected much later but eight days seems to be the time
    after which most people are culture negative, as also reported by
    \citet{Singanayagam2020}.}

\subsubsection{Duration of Symptoms}

We use the duration to recovery of mild and moderate cases reported by \cite[Figure~S3,
Panel~2]{Bi2020} for the duration of symptoms for asymptomatic and non-ICU requiring
symptomatic cases.

These numbers are only used for mild cases. We do not disaggregate by age. Note that the
length of symptoms is not very important in our model given that individuals stop being
infectious before their symptoms cease.

\subsubsection{Time from Symptom Onset to Admission to ICU}

The data on how many percent of symptomatic patients will require ICU is pretty thin. We
rely on data by the US CDC (\citet{Stokes2020}) and \href{https://bit.ly/3yKXFyu}{the
OpenABM-Project}. Table~\ref{tab:symptomatic-to-ICU} shows our derivations for the
probabilities of requiring intensive care per age group.

@@

For those who will require intensive care we follow \citet{Chen2020} who estimate the
time from symptom onset to ICU admission as 8.5 $\pm$ 4 days.

This aligns well with numbers reported for the time from first symptoms to
hospitalization: \citet{Gaythorpe2020} report a mean of 5.76 with a standard deviation
of 4. This is also in line with the durations collected by
\href{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Steckbrief.html#doc13776792bodyText16}{the
Robert-Koch-Institut}.

We assume that the time between symptom onset and ICU takes 4, 6, 8 or 10 days with
equal probabilities. These times mostly matter for the ICU capacities.

\subsubsection{Death and Recovery from ICU}

We take the survival probabilities and time to death and time until recovery from
intensive care from the \href{https://tinyurl.com/y5owhyts}{OpenABM Project}.

They report time until death to have a mean of 11.74 days and a standard deviation of
8.79 days. Approximating this with the normal distribution, we have nearly 10\%
probability mass below 0. We use it nevertheless as several other distributions (such as
chi squared and uniform) were unable to match the variance. Discretizing the
distribution leads to 41\% of individuals who will die from Covid-19 after one day in
intensive care, 22\% day after 12 days, 29\% after 20 days and 7\% after 32 days. Again,
we rescale this for every age group among those that will not survive.

They report a mean duration of 18.8 days until recovery and a standard deviation of
12.21 days. Approximating this with the normal distribution, we have over 5\%
probability mass below 0. Of those who recover in intensive care, 22\% do so
after one day, 30\% after 15 days, 28\% after 25 days and 18\% after 45 days.

>>>>

% Duration until Infectiousness and Symptoms ----------------------------------

@@

% Duration of Infectiousness ----------------------------------------------------------

We assume that the duration of infectiousness is the same for both symptomatic and
asymptomatic individuals as evidence suggests little differences in the transmission
rates between symptomatic and asymptomatic patients (\citet{Yin2020}) and that the viral
load between symptomatic and asymptomatic individuals are similar (\citet{Zou2020},
\citet{Byrne2020}, \citet{Singanayagam2020}). Our distribution of the duration of
infectiousness is based on \citet{Byrne2020}. For symptomatic cases they arrive at zero
to five days before symptom onset (see their figure 2) and three to eight days of
infectiousness afterwards.\footnote{Viral loads may be detected much later but eight days
seems to be the time after which most people are culture negative, as also reported by
\citet{Singanayagam2020}.} Thus, we arrive at 0 to 13 days as the range for
infectiousness among individuals who become symptomatic (see also figure 5).

% Duration of Symptoms ----------------------------------------------------------

We use the duration to recovery of mild and moderate cases reported by \cite[Figure~S3,
Panel~2]{Bi2020} for the duration of symptoms for non-ICU requiring symptomatic cases. We
only disaggregate by age how likely individuals are to require intensive
care.\footnote{The length of symptoms is not very important in our model given that
individuals mostly stop being infectious before their symptoms cease.}

% Time from Symptom Onset to Admission to ICU ------------------------------------------

For the time from symptom onset until need for intensive care we rely on data by the US
CDC (\citet{Stokes2020}) and \href{https://bit.ly/3yKXFyu}{the OpenABM-Project}.
Table~\ref{tab:symptomatic-to-ICU} shows our derivations for the probabilities of
requiring intensive care per age group.

@@

For those who will require intensive care we follow \citet{Chen2020} who estimate the
time from symptom onset to ICU admission as 8.5 $\pm$ 4 days. This aligns well with
numbers reported for the time from first symptoms to hospitalization:
\citet{Gaythorpe2020} report a mean of 5.76 with a standard deviation of 4. This is also
in line with the duration estimates collected by
\href{https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Steckbrief.html#doc13776792bodyText16}{the
Robert-Koch-Institut}. We assume that the time between symptom onset and ICU takes 4, 6,
8 or 10 days with equal probabilities. As we do not model nursing homes, do not focus on
matching deaths and do not use the number of individuals in intensive care to estimate
our parameters, these numbers are not important for our empirical results.

% Death and Recovery from ICU ----------------------------------------------------------

We take the survival probabilities and time to death and time until recovery from
intensive care from the \href{https://tinyurl.com/y5owhyts}{OpenABM Project}. They report
time until death to have a mean of 11.74 days and a standard deviation of 8.79 days. To
match this approximately we discretize that 41\% of individuals who will die from
Covid-19 do so after one day in intensive care, 22\% day after 12 days, 29\% after 20
days and 7\% after 32 days. Again, we rescale this for every age group among those that
will not survive. For survivors the \href{https://tinyurl.com/y5owhyts}{OpenABM Project}
reports a mean duration of 18.8 days until recovery and a standard deviation of 12.21
days. We discretize this such that of those who recover in intensive care, 22\% do so
after one day, 30\% after 15 days, 28\% after 25 days and 18\% after 45 days.
